Peer-to-Peer 6502 Cellular Automata

### 2018-07-03 paper.tex
removed quotes
CA

\section{Cellular Automaton}

@@

Each cell has 256 bytes (one page) of state.
All cells' bytes are initially zero, unless otherwise specified
(including, implicitly, cells whose coordinates are outside the CA; see also Section~\ref{sec:Blankets}).
These bytes are the storage of the virtual machine.

@@

\subsection{Blankets}
\label{sec:Blankets}

@@

We refer to these cells as the {\bf blanket} of the CA.
Earlier, in Section~\ref{sec:Storage}, we specified that the state of these cells was implicitly initialized to zero.
More generally, we may refer to the initial (and perpetual, throughout the execution of an update)
state of these cells as the CA's {\bf blanket state}.
This blanket state is zero until otherwise specified, but may be affected
by interactions with neighboring CAs in the infinite vector space,
as for example by the blockchain of Section~\ref{sec:Blockchain}.

@@

The CA has an associated blockchain, defined as in \cite{Nakamoto2008}.
Updates are incentivized by mining,
and the reward for mining is adjusted to include redemption of coins mined by adjacent CA blockchains
(this also updates the blanket cells accounted for by those CAs).

@@

\subsection{Writes}

@@

\subsection{Adjacencies}

The block may include sections of blockchain from {\bf adjacent cellular automata},
defined to be CAs with co-ordinates containing cells that
overlap with the current CA's blanket,
but no cells that overlap with
cells in the co-ordinate range of this CA (or any other CA previously encountered in the blockchain,
except the adjacent CA itself).
These blockchain segments from adjacent CAs are called {\bf adjacent segments}.

@@

When a block includes an adjacent segment, the CA's blanket is updated to reflect the state
of the blanket cells described by the adjacent segment.
Regular inclusion of adjacent segments from an adjacent CA's blockchain
corresponds to keeping a bidirectional read-only interface open with that CA.

@@

% Tables
\begin{table}
\begin{tabular}{llll}
  \hline
  From & To & Type & Contents \\
  \hline
  \hex{0000} & \hex{00FF} & RAM (storage-mapped) & State of cell $(x,y,z)$ \\
  \hex{0100} & \hex{01FF} & RAM (transient) & Stack, initialized to zero \\
  \hex{0200} & \hex{03FF} & RAM (transient) & ``Scratch'' memory, initialized to zero \\
  \hex{0400} & \hex{0401} & ROM (emulator-mapped) & {\tt TIMELEFT}: cycles left before termination \\
  \hex{0402} & \hex{3FFF} & Reserved & Read-only, zero \\
  \hex{4000} & \hex{7FFF} & RAM (storage-mapped) & Memory-mapped neighborhood (Table~\ref{tab:MooreNeighborhood}) \\
  \hex{8000} & \hex{FFFF} & ROM & Read-only (operating system) \\
  \hline
\end{tabular}
\caption{
  \label{tab:MemoryMap}
  Memory map for the 6502 virtual machine of cell $(x,y,z)$.
}
\end{table}

\begin{table}
\mooremap
\caption{
  \label{tab:MooreNeighborhood}
  Memory map for the 6502 virtual machine of cell $(x,y,z)$,
  using the 26-cell three-dimensional Moore neighborhood.
  All address ranges not defined in this table are read-only and zero;
  writing to these addresses has no effect.
  Pages mapping to cells outside the CA (e.g. $x<\alpha_x$ or $x \geq \alpha_x+L$, or similarly for $y,z$)
  are read-only and zero (unless otherwise specified, as in Section~\ref{sec:Blankets}).
  Writing to these addresses has no effect.
}
\end{table}

>>>>

\section{Cellular automata}

@@

Each cell has 256 bytes (one page) of state.
All cells' bytes are initially zero, unless otherwise specified
(including, implicitly, cells whose coordinates are outside the CA; see also Section~\ref{sec:AdjacentCells}).
These bytes are the storage of the virtual machine.

@@

\subsection{Adjacent cells}
\label{sec:AdjacentCells}

@@

We refer to these cells as the CA's {\bf adjacent cells}.
Earlier, in Section~\ref{sec:Storage}, we specified that the state of these cells was implicitly initialized to zero.
More generally, we may refer to the initial (and perpetual, throughout the execution of an update)
state of these cells as the CA's {\bf adjacent state}.
This adjacent state is zero until otherwise specified, but may be affected
by interactions with neighboring CAs in the infinite vector space,
as for example by the blockchain of Section~\ref{sec:Blockchain}.

@@

The CA has an associated blockchain, defined as in \cite{Nakamoto2008}.
Updates are incentivized by mining,
and the reward for mining is adjusted to include redemption of coins mined by adjacent CA blockchains
(this also updates the adjacent cell states accounted for by those CAs).

@@

\subsection{Write operations}

@@

\subsection{Adjacent segments}

The block may include sections of blockchain from {\bf adjacent cellular automata},
defined to be CAs with co-ordinate ranges that
overlap with the current CA's adjacent cells,
but no cells that overlap with
cells in the co-ordinate range of this CA (or any other CA previously encountered in the blockchain,
except the adjacent CA itself).
These blockchain segments from adjacent CAs are called {\bf adjacent segments}.

@@

When a block includes an adjacent segment, the CA's adjacent cell state is updated to match the adjacent segment.
Regular mutual inclusion of adjacent segments from adjacent CAs' blockchains
corresponds to keeping a bidirectional read-only interface open between those CAs.

@@

% Tables
\begin{table}
\begin{tabular}{llll}
  \hline
  From & To & Type & Contents \\
  \hline
  \hex{0000} & \hex{00FF} & RAM (storage-mapped) & State of cell $(x,y,z)$ \\
  \hex{0100} & \hex{01FF} & RAM (transient) & Stack, initialized to zero \\
  \hex{0200} & \hex{03FF} & RAM (transient) & Scratch memory, initialized to zero \\
  \hex{0400} & \hex{0401} & ROM (emulator-mapped) & {\tt TIMELEFT}: cycles left before termination \\
  \hex{0402} & \hex{3FFF} & Reserved & Read-only, zero \\
  \hex{4000} & \hex{7FFF} & RAM (storage-mapped) & Memory-mapped neighborhood (Table~\ref{tab:MooreNeighborhood}) \\
  \hex{8000} & \hex{FFFF} & ROM & Read-only (operating system) \\
  \hline
\end{tabular}
\caption{
  \label{tab:MemoryMap}
  Memory map for the 6502 virtual machine of cell $(x,y,z)$.
}
\end{table}

\begin{table}
\mooremap
\caption{
  \label{tab:MooreNeighborhood}
  Memory map for the 6502 virtual machine of cell $(x,y,z)$,
  using the 26-cell three-dimensional Moore neighborhood.
  All address ranges not defined in this table are read-only and zero;
  writing to these addresses has no effect.
  Pages mapping to cells outside the CA (e.g. $x<\alpha_x$ or $x \geq \alpha_x+L$, or similarly for $y,z$)
  are read-only and zero (unless otherwise specified, as in Section~\ref{sec:AdjacentCells}).
  Writing to these addresses has no effect.
}
\end{table}
